Presentasjon OPX Fiffig tittel

### 2022-08-03 Presentasjon/presentasjon.Rmd
Nye stikkord

## <br> Phase 1 – how to harvest and analyze the data?
- A webcrawler that could collect data across different websites? <br> This would be too difficult and it would only work with some organizations
- A code that could read PDF? <br>

## <br> Phase 2 – Exploring three options
- Financial statements in yearly reports published as PDF <br>
Issue: Financial statements are not always published as text
- Webscraping financial statements from Proff.no <br>
Issue: Proff.no does not allow webscraping!
- Webscraping the Brønnøysund registry <br>
Issue: The registry does offer API access, but access costs about 500k kr

## <br> Workarounds... 
- Proff.no: It maaay be legal to manually download the websites as HTML instead of scraping 
- Brønnøysund: We attempted to request a temporary access to XML documents

## <br> ... and why they did not work
- Different accounting divisions at Proff.no and Brønnøysund prohibited extracting the correct sums  OPX wanted
- Not all NGOs publish their financial statements and certainly not for every year
- **Which led us to Phase 3 - scrapping the scraping**

@@

# Data collection

# Data description

>>>>

## <br> Phase 1 – how to harvest and analyze the data?
- OPX wanted us to harvest data --> how? <br> 
- A webcrawler? <br> 
- No: Would not work for every organization <br> 
- A code that could read PDF? <br> 
- Perhaps: Financial statements as text tables and as images

## <br> Phase 2 – Exploring three options
- 1. Reading PDFs <br>
Issue: Not always published as text
- 2. Webscraping from Proff.no <br>
Issue: Proff.no does not allow webscraping
- 3. Webscraping the Brønnøysund registry <br>
Issue: No API access, and access costs ~ kr 500K

## <br> Workarounds... 
- Proff.no: Download HTML?
- Brønnøysund: Request temporary access

## <br> ... and why they did not work
- Different accounting items used
- Incomplete financial reporting from NGOs

- **Which led us to Phase 3 - scrapping the scraping**

@@

## <br> Phase 3 – Scrapping the scraping
- OPX wanted KPIs <br>
- Found useful KPIs <br>
- Created an interactive dashboard

## <br> Data collection & data description
- Used data from OPX and Proff.no <br>
- OPX: From their webpage. <br>
- Used to create KPIs and check our codes <br>
- Proff.no: Downloaded HTML documents. <br>
- Used to create visualizations.
